Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
another pass

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: when one is or is not we are given a target loss and when one is making a continuous or discrete prediction.
\raft{This is a nice way to frame the four settings.  I think the first paragraph just has to tee this up, without necessarily going into as much detail on the continuous prediction setting}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.

\paragraph{Notation}
\raf{Yeah, I think this is a bit too long.  And as a reader I would not know what to expect to find here vs section 2.  Things like $\supp,\affhull,2^\R$ make sense to define here in a very terse paragraph, the same length as this comment, but I'd suggest moving the rest to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}

@@

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}

@@

In order to study the difficulty of a learning problem, various works have studied the minimum input dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).

@@

\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}

>>>>

\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green!80!blue}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{[BTW: #1]}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'm usually against these sorts of sections if they are truly just a roadmap.  See if you can make it flow less like a table of contents and more like a list of contributions with references to where in the paper to find them.  E.g.\ ``After reviewing previous work and introducing our notation (\S X) we lay down a new general definition of consistency which can simultaneously capture all four settings above (\S Y).''} \jessiet{Took a pass; let me know if this is better.} \raft{Exactly, well done}
%actually tell the reader
After reviewing previous work and tools to study consistency (\S~\ref{sec:related-work}), we lay down a new general definition of consistency which can simultaneously capture all four settings mentioned above (\S~\ref{sec:consis-implies-indir}).
Our main result (\S~\ref{sec:char-convex}, Theorem~\ref{thm:cvx-flats}) characterizes
\raft{Not a characterization!}
the existence of consistent convex surrogates in a given dimension $d$.
This result is closely related to those provided by~\cite[Theorem 16]{ramaswamy2016convex} in the discrete prediction setting; in fact, we show their result is a special case of our main result (Corollary~\ref{cor:fsd-bound}).
Moreover, in continuous settings, one often has a prediction task for which they want to construct a consistent convex loss, rather than an original loss.
Property elicitation is the main tool to understand consistency dimension in this case, and insights from our main result answer an open question posed by~\cite[Section 8]{frongillo2018elicitation}.

\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}

@@

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}

@@

In order to study the difficulty of a learning problem, various works have studied the minimum prediction dimension $d$ needed in order to construct a consistent surrogate loss $L: \reals^d \times \Y \to \reals$, typically through proxies such as calibration (\cite{ramaswamy2016convex}) and property elicitation (\cite{frongillo2015vector-valued,fissler2015higher,frongillo2018elicitation}).

@@

\bo{Where do we discuss the chain from consistency to indirect elicitation ... how much to talk about our general calibration definition, and general consistency definitions?}
\raf{Should be in section 3}
